### 2020-05-31 report/sections/evalconcl/eval/benchmarks.tex
Report: benchmark

Relative to the two \texttt{bare} implementations, the
\texttt{mpst} implementation shows more consistency.

@@

\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{\textwidth}
\centering
\begin{lstlisting}[language=javascript,tabsize=2]
socket.onmessage = ({ data }) => {
	const { label, payload } = JSON.parse(data.toString());
	if (label === 'PING') {
		let count: number = payload[0];
		console.timeLog(LABEL, ++count);
		if (count === MSGS) {
			socket.send(JSON.stringify({
				label: 'BYE',
				payload: [count],
			}));
		} else {
			socket.send(JSON.stringify({
				label: 'PONG',
				payload: [count],
			}));
		}
	} else {
		throw new Error(`Unrecognised label: ${label}`)
	}
}
\end{lstlisting}
\caption{\texttt{bare}}
\label{lst:nodepingpongbare}
\end{subfigure}
\hfill
\begin{subfigure}[b]{\textwidth}
\centering
\begin{lstlisting}[language=javascript,tabsize=2]
// NOTE: `Implementation' namespace omitted for brevity.

const logic = new Initial({
	PING: (count) => {
		console.timeLog(LABEL, ++count);
		if (count === MSGS) {
			return new S16([Labels.S16.BYE, [count], new Terminal()]);
		} else {
			return new S16([Labels.S16.PONG, [count], logic]);
		}
 	}
});
\end{lstlisting}
\caption{\texttt{mpst}}
\label{lst:nodepingpongmpst}
\end{subfigure}
\captionof{figure}{Comparison of \trole{Svr} implementations in benchmark}
\label{fig:nodepingpong}
\end{figure}

>>>>

Relative to the two \texttt{bare} implementations, the
\texttt{mpst} version performs more consistently, perhaps as a result
of the session runtimes handling all WebSocket interactions in a
systematic way. The gradient of the graph represents the rate at which
a Ping-Pong round trip takes place. 
We observe a steeper gradient when the protocol begins, 
which illustrates the overhead incurred in the 
session joining phase in our generated APIs.
Aside from these factors, all three implementations generally share
similar characteristics in their protocol execution.

@@

\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{\textwidth}
\centering
\begin{lstlisting}[language=javascript,tabsize=2]
socket.onmessage = ({ data }) => {
	const { label, payload } = JSON.parse(data.toString());
	if (label === 'PING') {
		let count: number = payload[0];
		console.timeLog(LABEL, ++count);
		if (count === MSGS) {
			socket.send(JSON.stringify({
				label: 'BYE',
				payload: [count],
			}));
		} else {
			socket.send(JSON.stringify({
				label: 'PONG',
				payload: [count],
			}));
		}
	} else {
		throw new Error(`Unrecognised label: ${label}`);
	}
}
\end{lstlisting}
\caption{\texttt{bare} implementation of Ping Pong \trole{Svr}}
\label{lst:nodepingpongbare}
\end{subfigure}
\hfill
\begin{subfigure}[b]{\textwidth}
\centering
\begin{lstlisting}[language=javascript,tabsize=2]
// NOTE: `Implementation' namespace omitted for brevity.

const logic = new S14({
	PING: (count) => {
		console.timeLog(LABEL, ++count);
		if (count === MSGS) {
			return new S16([Labels.S16.BYE, [count], new S15()]);
		} else {
			return new S16([Labels.S16.PONG, [count], logic]);
		}
 	}
});
\end{lstlisting}
\caption{\texttt{mpst} implementation of Ping Pong \trole{Svr}}
\label{lst:nodepingpongmpst}
\end{subfigure}
\captionof{figure}{Comparison of \texttt{bare} and \texttt{mpst}
implementations for Ping Pong \trole{Svr}}
\label{fig:nodepingpong}
\end{figure}
